Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-05-31 GWLDCII.tex
from Susama: Read through section 5. Added exposition. Have lots of questions.

The results of Section~\ref{sec GN algorithm} allow us to relate the position of propagators in a Wilson loop diagram $W$ to minors of $C(W)$, which we use in this section to understand the denominator of the integral $I(W)$ associated to a Wilson loop diagram (see Definition~\ref{def R(W)}).

@@

\begin{algorithm}\label{alg WLD to denom via GN}
Let $W = (\cP,n)$ be a Wilson loop diagram, and let $C(W)$ be the matrix of $W$ as defined in \eqref{C(W) dfn} (see Section~\ref{section WLD background}).
\begin{itemize}
  \item For each $i \in [n]$, we construct a factor $r_i$ as follows:
    \begin{itemize}
      %\item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i-1$st Grassmann necklace element, $I_{i-1}$.  (By convention set $I_{-1}=I_n$.)  Write $I_{i-1}(p)$ for the vertex associated to propagator $p$ under this bijection.
      %\item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i$th Grassmann necklace element, $I_{i}$.  Write $I_{i}(p)$ for the vertex associated to propagator $p$ under this bijection.
      \item Let $S_i = \{p \in \cP \ | \ I_{i-1}(p) \neq I_i(p)\}$. (By convention, set $I_{-1} = I_n$.)
	  %\item Write $\Delta_{I_i}$ for the determinant of the $k \times k$ minor of $C(W)$ with columns indexed by $I_i$.
      \item Let $r_i$ be the determinant of the $|S_i|\times |S_i|$ minor of $C(W)$ with rows indexed by $S_i$ and columns indexed by $I_i(S_i)$.  %$\Delta_{I_i}$ with all variables from rows associated to $p\not\in S_i$ set to $1$.
    \end{itemize}
  \item Define $R = \prod_{i=1}^n r_i$.
\end{itemize}
\end{algorithm}

@@

As we take each $r_i$ to simply be the determinant of a particular submatrix of $C(W)$, the sign of each $r_i$ is well-defined.  The goal is to show that $R$ is equal to the denominator of the Wilson loop diagram as defined in Definition~\ref{def R(W)}.
%  However, we will not be interested in these signs as they only contribute an overall sign to $R$ and our main theorem in this section (Theorem~\ref{thm denom}) will simply be to show that $R$ is equal up to a $\mathbb{Q}$-multiple to the denominator of the Wilson loop diagram (see Definition~\ref{def R(W)}).

@@

\begin{eg}
Consider the Wilson loop diagram in Figure~\ref{fig R eg}. Assigning propagators $p$, $q$, $s$ to rows $1,2,3$ respectively, we obtain the matrix
\[
C(W) = \begin{bmatrix} a & b & 0 & 0 & 0 & c & d \\ e & f & 0 & 0 & g & h & 0 \\ i & j & 0 & k & l & 0 & 0 \end{bmatrix}
\]
The Grassmann necklace of this diagram is 
\begin{gather*}I_1 = \{1,2,4\}, I_2 = \{2,4,5\}, I_3 = \{4,5,6\}, I_4=\{4,5,6\},\\ I_5=\{5,6,7\}, I_6 = \{6,7,1\}, I_7=\{7,1,2\}. \end{gather*}  
Figure~\ref{fig R eg} indicates the pairings between propagators and vertices for each $i \in [1,7]$.

From $I_1$ to $I_2$, the propagators $p$ and $q$ change which vertex they are assigned to but $r$ is assigned to vertex 4 in both, so $S_2 = \{p,q\}$.  Then
\[
\Delta_{I_2}=\det\begin{bmatrix} b & 0 & 0 \\ f & 0 & g \\ j & k & l \end{bmatrix} = kgb, \qquad r_2 = \det\begin{bmatrix} b & 0 & 0 \\ f & 0 & g \\ 1 & 1 & 1 \end{bmatrix} = gb.
\]
where the 1s in the third row of the second matrix correspond to the fact that $I_1(s) = I_2(s)$.  Continuing likewise, we get $r_3 = c$, $r_4=1$ (since $I_4 = I_3$), $r_5 = lhd$, and $r_6 = i$.

At $I_7$ the situation is more complicated: we have $S_7 = \{q,s\}$, so we find that $\Delta_{I_7} = d(ej-fi)$ and $r_7 = ej-fi$. This quadratic factor corresponds to the fact that $q$ and $s$ share an edge {\em and} contribute both endpoints of that edge to $I_7$; see Proposition~\ref{prop alg gives rad} below.

@@

@@

\begin{proof}
\begin{enumerate}
    \item The nonzero entries of $C(W)$ are independent indeterminates and so every $i\times i$ minor of $C(W)$ is either homogeneous of degree $i$ or is $0$.  Thus each $\Delta_{I_i}$ and each $r_i$ is homogeneous.  %Furthermore, each row contributes one factor to each term in the expansion of $\Delta_{I_i}$ so the result of setting the variables from a subset of rows to $1$ is still homogeneous.  Thus each $r_i$ is homogeneous.
    \item Using the expression for the determinant as a sum over permutations we see that $\Delta_{I_i}$ is a sum over bijections between $I_i$ and $\mathcal{P}$.  The nonzero terms in this sum are precisely those bijections such that each propagator is associated to one of its supporting vertices in $I_i$, since only those locations in $C(W)$ are nonzero.  Since the nonzero entries of $C(W)$ are independent there can be no cancellation between terms in this expansion.

@@

{\em Proof of claim}: By the structure of determinants we know that $\Delta_{I_i} = fg$, where $g$ involves only variables associated to propagators not in $\mathcal{P}'$ and associated to vertices not in $J$.

Expanding out $fg$ yields a signed sum of monomials. In each of these monomials, $f$ contributes those variables associated both to a propagator in $\mathcal{P}'$ and to a vertex in $J$, and $g$ contributes those variables associated both to a propagator not in $\mathcal{P}'$ and to a vertex not in $J$, and no other variables appear.

@@

All that remains is to prove that $\Delta_{I_i}$ has no irreducible factors of degree 3 or more.  Suppose for a contradiction that $f$ is a factor of $\Delta_{I_i}$ of degree $\geq 3$. Note that by removing the propagators which come before those contributing to $f$ and changing $i$ to be the first vertex which contributes to $f$, we obtain a different admissible diagram for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and
$i$ contributes to $f$.  Showing that this different admissible diagram gives a contradiction is sufficient, and so we may assume that $i\in I_i$ and $i$ contributes to $f$.  Finally, we can suppose that $W$ is minimal in number of propagators with the above occuring.

@@

Let $S$ be the set of propagators inside $p$ along with $p$ itself. $I_i$ and $I_{i+1}$ can only differ once $p$ contributes to $I_{i+1}$, so $I_i(q) = I_{i+1}(q)$ for each $q \in S \backslash \{p\}$. Thus if a propagator contributes $m$ in $I_i$ then it must lie outside $p$.

If neither $m$ nor $m+1$ appear in $I_i$ then by Corollary~\ref{no coloops} $V(p) \cap I_i = \{i\}$, and so the row of $p$ in the matrix of $\Delta_{I_i}$ has only one nonzero entry; hence $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$, which is a contradiction.  So we must have at least one of $m$ and $m+1$ in $I_i$.  However, all propagators in $S$ are mapped by the function $I_{i}(\cdot)$ to vertices strictly before $m$, so the matrix giving $\Delta_{I_i}$ has the form
\[
\begin{bmatrix} A & B \\ 0 & C\end{bmatrix}
\]
where $A$ is the $|S|\times |S|$ matrix indexed by the propagators in $S$ and the vertices in $I_i(S)$. No other propagators can be supported on these vertices since all other propagators are outside of $p$, and $p$ is the first propagator supported at $i$; this explains the zero block.  Therefore $\Delta_{I_i} = \det A \det C$, and both factors are nontrivial since at least one of $m$ and $m+1$ appear in $I_i$.  If we remove the propagator outside of $p$ that contributes $m$ or $m+1$, we get a smaller diagram for which $\Delta_{I_i} = \det A$. This contradicts the minimality of our choices unless $\det A$ is quadratic, which in turn contradicts our assumption that $i$ and $p$ contribute to an irreducible factor $f$ of degree at least 3.

\textbf{Case 2}: Suppose $p$ has one end on the edge $(i, i+1)$.  If no other propagators are supported on $i$ then the column of $C(W)$ corresponding to vertex $i$ has only one nonzero entry in it, and so $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$; as above, this is a contradiction.  Thus we can take $q$ to be the propagator such that $I_i(q)=i+1$. We know that $q$ has one end on the edge $(i, i+1)$ and is adjacent to $p$ on that edge in the counterclockwise direction (see Figure \ref{fig no big factors}).  Write $(i, i+1, j, j+1)$ for the support of $q$.  The situation for $q$ is very similar to case 1: in particular, we have $I_{i+1}(q) = j$ by Lemma~\ref{vertex cyclic int lem} and so if $j\in I_i$ then the propagator which contributes $j$ is outside of $q$.

Similarly to Case 1, let $S$ be the set of propagators inside $q$ along with $p$ and $q$ themselves. Then all propagators in $S$ are mapped by $I_i(\cdot)$ to vertices strictly before $j$ and no other propagators are supported on vertices strictly before $j$.  Thus the matrix giving $\Delta_{I_i}$ has the form
\[
\begin{bmatrix} A & B \\ 0 & C\end{bmatrix}
\]
where $A$ is the submatrix indexed by the propagators in $S$ and the vertices in $I_i(S)$. Again two things can now happen.  If some vertex $j$ or larger (with respect to $>_i$) belongs to $I_i$ then $B$ and $C$ are at least one column wide, and so the block form of the matrix gives a nontrivial factorization of $\Delta_{I_i}$.  This yields a contradiction as in Case 1: either $W$ contains unnecessary propagators which contradicts our minimality assumption, or $\det A$ is quadratic which contradicts the assumption that $p$ and $i$ contribute to $f$, an irreducible factor of degree at least 3.

@@

\item Suppose propagators $p$ and $q$ are supported on a common edge $(a,b)$, with $I_i(p)=a$ and $I_i(q)=b$.  Let $x_{p,a},x_{p,b},x_{q,a},x_{q,b}$ be the associated variables in $C(W)$. For any fixed bijection $\sigma$ from $\cP-\{p,q\}$ to $I_i -\{a,b\}$ for which each propagator is supported on its image under the bijection, we can extend $\sigma$ to a bijection of all propagators with $I_i$ in two ways: either $p\mapsto a$ and $q\mapsto b$ or $p\mapsto b$ and $q\mapsto a$.  The sum of the contributions of all these bijections to $\Delta_{I_i}$ is therefore the product of $x_{p,a}x_{q,b}-x_{p,b}x_{q,a}$ with the minor coming from $\cP-\{p, q\}$ and $I_i - \{a,b\}$.  Since there is no cancellation of terms in the expansion of $\Delta_{I_i}$, if any other terms appear then they will cause a factor which is not in the form described in the previous part.  Therefore no such terms exist and $x_{p,a}x_{q,b}-x_{p,b}x_{q,a}$ is a factor of $\Delta_{I_i}$.

@@

\begin{thm}\label{thm denom}
  Given any admissible Wilson loop diagram $W$, let $\{I_1, \ldots I_n\}$ be the associated Grasmann necklace. Then the denominator of the integral, $R(W)$ (see Definition~\ref{def R(W)}), is the $R$ of Algorithm~\ref{alg WLD to denom via GN}, which is also, up to scalar multiple, the radical of $\prod_{i=1}^n \Delta_{I_i}$, where $\Delta_{I_i}$ is the determinant of the $k \times k$ minor indicated by $I_i$.  
\end{thm}

\note{Note that there is still a mention of scalar multiple in this theorem because it seems to me that the def of radical is only up to scalar multiple, but the part relating $R(W)$ to $R$ is exact with no scalar multiples.}

@@

Finally then we need to check the scalar.  By Definition~\ref{def R(W)} each linear factor appears with coefficient $1$ and each $2\times 2$ deteriminant factor appears with the same sign as the determinant of the corresponding minor in $C(W)$.  Therefore $R=R(W)$.
\end{proof}

***explain why this result was interesting***

>>>>

In this section, we investigate the poles of the integrand for $I(W)$, that is $R(W)$ as defined in Definition~\ref{def R(W)}. It is conjectured that for a fixed number of propagators and a given set of external twistors $\cZ$, [cite] \bas \sum_{W | |\cP| = k} I(W)(\cZ) <\infty \;.\eas In otherwords, all poles of the intergrals must cancel. As a step towards this, in this section, we prove some results about $R(W)$.

The results of Section~\ref{sec GN algorithm} allow us to relate the position of propagators in a Wilson loop diagram $W$ to minors of $C(W)$, $R(W)$.

@@

\begin{algorithm}\label{alg WLD to denom via GN}
Let $W = (\cP,n)$ be a Wilson loop diagram, and let $C(W)$ be the matrix of $W$ as defined in \eqref{C(W) dfn} with a fixed ordering on $\cP$. (see Section~\ref{section WLD background}).
\begin{itemize}
  \item For each $i \in [n]$, we construct a factor $r_i$ as follows:
    \begin{itemize}
      %\item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i-1$st Grassmann necklace element, $I_{i-1}$.  (By convention set $I_{-1}=I_n$.)  Write $I_{i-1}(p)$ for the vertex associated to propagator $p$ under this bijection.
      %\item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i$th Grassmann necklace element, $I_{i}$.  Write $I_{i}(p)$ for the vertex associated to propagator $p$ under this bijection.
      \item Let $S_i = \{p \in \cP \ | \ I_{i-1}(p) \neq I_i(p)\}$. (By convention, set \hlfix{$I_{0} = I_n$}{changed. correct?}.)
	  %\item Write $\Delta_{I_i}$ for the determinant of the $k \times k$ minor of $C(W)$ with columns indexed by $I_i$.
      \item Let $r_i$ be the determinant of the $|S_i|\times |S_i|$ minor of $C(W)$ with rows indexed by $S_i$ and columns indexed by $I_i(S_i)$.  %$\Delta_{I_i}$ with all variables from rows associated to $p\not\in S_i$ set to $1$.
    \end{itemize}
  \item Define $R = \prod_{i=1}^n r_i$.
\end{itemize}
\end{algorithm}

\hlfix{That is, each $r_i$ is the determinant of the minor determined by the propagators (rows) that contribute different values (columns) to the $i^{th}$ element of the Grassmann necklace than they did to the $i-1^{th}$.}{added. accurate?}

@@

As we take each $r_i$ to simply be the determinant of a particular submatrix of $C(W)$, the sign of each $r_i$ is well-defined.  Before proving the main results of this section, we given an illustrative example. Below, we show that $R$ is equal to the denominator of the Wilson loop diagram as defined in Definition~\ref{def R(W)}, and is the radical of the product $\prod_{i=1}^n \Delta_{I_i}$.
%  However, we will not be interested in these signs as they only contribute an overall sign to $R$ and our main theorem in this section (Theorem~\ref{thm denom}) will simply be to show that $R$ is equal up to a $\mathbb{Q}$-multiple to the denominator of the Wilson loop diagram (see Definition~\ref{def R(W)}).

@@

\begin{eg}
Consider the Wilson loop diagram in Figure~\ref{fig R eg}. Assigning propagators $p$, $q$, $s$\todo{$s = r$ in pictures} to rows $1,2,3$ respectively, we obtain the matrix
\[
C(W) = \begin{bmatrix} a & b & 0 & 0 & 0 & c & d \\ e & f & 0 & 0 & g & h & 0 \\ i & j & 0 & k & l & 0 & 0 \end{bmatrix}
\]
The Grassmann necklace of this diagram is 
\begin{gather*}I_1 = \{1,2,4\}, I_2 = \{2,4,5\}, I_3 = \{4,5,6\}, I_4=\{4,5,6\},\\ I_5=\{5,6,7\}, I_6 = \{6,7,1\}, I_7=\{7,1,2\}. \end{gather*}  
Figure~\ref{fig R eg} indicates the pairings between propagators and vertices for each $i \in [1,7]$.

From $I_1$ to $I_2$, the propagators $p$ and $q$ change \hlfix{which vertex they are assigned to}{Can we change this language to which vertices they contribute?}. That is $I_1(p) = 1$, $I_1(q)= 2$ while $I_2(p) = 2$, $I_2(q)= 5$. However, $r$ contributes  4 to both $I_1$ and $I_2$, so $S_2 = \{p,q\}$.  Then
\[
\Delta_{I_2}=\det\begin{bmatrix} b & 0 & 0 \\ f & 0 & g \\ j & k & l \end{bmatrix} = kgb, \qquad r_2 = \det\begin{bmatrix} b & 0 & 0 \\ f & 0 & g \\ 1 & 1 & 1 \end{bmatrix} = gb.
\] {\color{violet} shouldn't $r_2$ be a $2 \times 2$ matrix? i.e. $r_2 = \det\begin{bmatrix} b & 0 \\ f &  g \end{bmatrix} = gb.$}
\hlfix{where the 1s in the third row of the second matrix correspond to the fact that $I_1(s) = I_2(s)$.}{This doesn't seem to match with what is said in the algorithm.}  Continuing likewise, we get $r_3 = c$, $r_4=1$ (since $I_4 = I_3$), $r_5 = lhd$, and $r_6 = i$.

At $I_7$ the situation \hlfix{is more complicated}{It seems to be exactly what we expect from the alg?}: we have $S_7 = \{q,s\}$ with $I_7(S_7) = \{ 1,2\}$, $\Delta_{I_7} = d(ej-fi)$ and $r_7 = ej-fi$.

Note that unlike the previous $r_i$, $r_7$ an irriducible quadratic factor. This corresponds to the fact that $q$ and $s$ share an edge {\em and} contribute both endpoints of that edge to $I_7$; see Proposition~\ref{prop alg gives rad} below.

@@

We are now ready to begin proving the main result of this section. We begin with a proposition stating several facts about $\Delta_{I_i}$ and their relationship to $r_i$.

@@

\begin{proof}
\begin{enumerate}
    \item The nonzero entries of $C(W)$ are independent indeterminates and so every $i\times i$ minor of $C(W)$ is either homogeneous of degree $i$ or is $0$.  Thus each $\Delta_{I_i}$ and each $r_i$ is homogeneous.  %Furthermore, each row contributes one factor to each term in the expansion of $\Delta_{I_i}$ so the result of setting the variables from a subset of rows to $1$ is still homogeneous.  Thus each $r_i$ is homogeneous.
    \item Using the expression for the determinant as a sum over permutations from Lemma \ref{lem basis as perm} we see that $\Delta_{I_i}$ is a sum over bijections between $I_i$ and $\mathcal{P}$.  The nonzero terms in this sum are precisely those bijections such that each propagator is associated to one of its supporting vertices in $I_i$, since only those locations in $C(W)$ are nonzero.  Since the nonzero entries of $C(W)$ are independent there can be no cancellation between terms in this expansion.

@@

{\em Proof of claim}: By the structure of determinants we know that $\Delta_{I_i} = fg$, where $g$ involves only variables associated to propagators not in $\mathcal{P}'$ and associated to vertices not in $J$.  \todo{Is the heart of this proof due to the fact that there are no cancelations? It feels tautological to me, but I'm clearly not following}

Expanding out $fg$ yields a signed sum of monomials. \hlfix{In each of these monomials, $f$ contributes those variables associated both to a propagator in $\mathcal{P}'$ and to a vertex in $J$, and $g$ contributes those variables associated both to a propagator not in $\mathcal{P}'$ and to a vertex not in $J$, and no other variables appear.  }{Isn't this redundant with the previous paragraph?}

@@

All that remains is to prove that $\Delta_{I_i}$ has no irreducible factors of degree 3 or more.  Suppose for a contradiction that $f$ is a factor of $\Delta_{I_i}$ of degree $\geq 3$. Note that by removing the propagators which come \hlfix{before}{ordering?} those contributing to $f$ and \hlfix{changing $i$ to be the first vertex}{does this generalize to other $i$?} which contributes to $f$, we obtain a \hlfix{different admissible diagram}{Is this just the diagram gotten by removing certain props?} for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and
$i$ contributes to $f$.  Showing that this different admissible diagram gives a contradiction is sufficient, and so we may assume that $i\in I_i$ and $i$ contributes to $f$.  Finally, we can suppose that $W$ is minimal in number of propagators with the above occuring.

@@

Let $S = \cP_{in}(p)$ be the set of propagators inside $p$ in the $<_i$ order. $I_i$ and $I_{i+1}$ can only differ once $p$ contributes to $I_{i+1}$, so $I_i(q) = I_{i+1}(q)$ for each $q \in S \backslash \{p\}$. Thus if a propagator contributes $m$ in $I_i$ then it must lie outside $p$.

If neither $m$ nor $m+1$ appear in $I_i$ then by Corollary~\ref{no coloops} $V(p) \cap I_i = \{i\}$, and so the row of $p$ in the matrix of $\Delta_{I_i}$ has only one nonzero entry; hence $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$, which \hlfix{is a contradiction}{Why? because $i$ contributes to $f$?}.  So we must have at least one of $m$ and $m+1$ in $I_i$.  However, all propagators in $S$ are mapped by the function $I_{i}(\cdot)$ to vertices strictly before $m$, so the matrix giving $\Delta_{I_i}$ has the form
\[
\begin{bmatrix} A & B \\ 0 & C\end{bmatrix}
\]
where $A$ is the $|S|\times |S|$ matrix indexed by the propagators in $S$ and the vertices in $I_i(S)$. No other propagators can be supported on these vertices since all other propagators are outside of $p$, and $p$ is the first propagator supported at $i$; this explains the zero block.  Therefore $\Delta_{I_i} = \det A \det C$, and both factors are nontrivial since at least one of $m$ and $m+1$ appear in $I_i$.  If we remove the propagator outside of $p$ that contributes $m$ or $m+1$, we get a smaller diagram for which $\Delta_{I_i} = \det A$ {\color{violet}why not $\det A \det C'$ with $C'$a minor of $C$?}. This contradicts the minimality of our choices unless $\det A$ is quadratic, which in turn contradicts our assumption that $i$ and $p$ contribute to an irreducible factor $f$ of degree at least 3.

\textbf{Case 2}: Suppose $p$ has one end on the edge $(i, i+1)$.  If no other propagators are supported on $i$ then the column of $C(W)$ corresponding to vertex $i$ has only one nonzero entry in it, and so $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$; as above, this is a contradiction.  Thus we can take $q$ to be the propagator such that $I_i(q)=i+1$. {\color{violet} How do we know this exists? Why can't we solve this by having $r$ supported on the $i-1^{th}$ edge?} We know that $q$ has one end on the edge $(i, i+1)$ and is adjacent to $p$ on that edge in the counterclockwise direction (see Figure \ref{fig no big factors}).  Write $(i, i+1, j, j+1)$ for the support of $q$.  The situation for $q$ is very similar to case 1: in particular, we have $I_{i+1}(q) = j$ by Lemma~\ref{vertex cyclic int lem} and so if $j\in I_i$ then the propagator which contributes $j$ is outside of $q$.

Similarly to Case 1, let \st{$S$ be the set of propagators inside $q$ along with $p$ and $q$ themselves.}{\color{violet}$S = \cP_{in}(q)$ in the $<_i$ order. Note that $p \in S$.}\hlfix{Then all propagators in $S$ are mapped by $I_i(\cdot)$ to vertices strictly before $j$ and no other propagators are supported on vertices strictly before $j$.}{???}  Thus the matrix giving $\Delta_{I_i}$ has the form
\[
\begin{bmatrix} A & B \\ 0 & C\end{bmatrix}
\]
where $A$ is the submatrix indexed by the propagators in $S$ and the vertices in $I_i(S)$. Again two things can now happen.  If some vertex $j$ or larger (with respect to $>_i$) belongs to $I_i$ then $B$ and $C$ are at least one column wide, and so the block form of the matrix gives a nontrivial factorization of $\Delta_{I_i}$.  This yields a contradiction as in Case 1: either $W$ contains unnecessary propagators which contradicts our minimality assumption, or $\det A$ is quadratic which contradicts the assumption that $p$ and $i$ contribute to $f$, an irreducible factor of degree at least 3.

@@

\item Suppose propagators $p$ and $q$ are supported on a common edge $(a,b)$, with $I_i(p)=a$ and $I_i(q)=b$.  Let $x_{p,a},x_{p,b},x_{q,a},x_{q,b}$ be the associated variables in $C(W)$. For any fixed bijection $\sigma$ from $\cP-\{p,q\}$ to $I_i -\{a,b\}$ for which each propagator is supported on its image under the bijection, we can extend $\sigma$ to a bijection of all propagators with $I_i$ in two ways: either $p\mapsto a$ and $q\mapsto b$ or $p\mapsto b$ and $q\mapsto a$.  The sum of the contributions of all these bijections to $\Delta_{I_i}$ is therefore the product of \hlfix{$x_{p,a}x_{q,b}-x_{p,b}x_{q,a}$}{why? terms in determinant come from bijections. Why should all bijections appear in det?} with the minor coming from $\cP-\{p, q\}$ and $I_i - \{a,b\}$.  Since there is no cancellation of terms in the expansion of $\Delta_{I_i}$, if any other terms appear then they will cause a factor which is not in the form described in the previous part.  Therefore no such terms exist and $x_{p,a}x_{q,b}-x_{p,b}x_{q,a}$ is a factor of $\Delta_{I_i}$.

@@

\begin{thm}\label{thm denom}
  Given any admissible Wilson loop diagram $W$, let $\{I_1, \ldots I_n\}$ be the associated Grasmann necklace. Then the denominator of the integral, $R(W)$ (see Definition~\ref{def R(W)}), is the $R$ of Algorithm~\ref{alg WLD to denom via GN}. Furthermore, the ideal generated by $R(W)$ is the radical of the ideal generated by $\prod_{i=1}^n \Delta_{I_i}$, where $\Delta_{I_i}$ is the determinant of the $k \times k$ minor indicated by $I_i$.  
\end{thm}

{\color{violet} Got rid of need for scalar multiples by talking about radicals.}

@@

Finally then we need to check the scalar.  By Definition~\ref{def R(W)} each linear factor appears with coefficient $1$ and each $2\times 2$ deteriminant factor appears with the same sign as the determinant of the corresponding minor in $C(W)$.  Therefore $R=R(W)$. \todo{I'm pretty sure that there isn't a sign issue here. But do we have a proof?}
\end{proof}

Thus we have shown a deep relationship between the physically derived poles of the integrals $I(W)$ and the geometry and combinatorics associated to the diagrams $W$. At the very least, this is yet another piece of circumstantial evidence indicating that the positroid representation of Wilson loop diagrams is the correct geometric object to be considering when considering the Wilson loop amplitudes geometrically.

While the authors cannot yet offer a proof that the appropriate sum of the Wilson loop diagrams are, in fact, finite, as conjectured [cite], we do hope that this relationship to the Grassmann Necklace elements will provide a different avenue for answering that and related questions.
